Efficient Calculation of Polynomial and Interaction Features on Sparse Matrices

### 2015-09-21 paper/paper2.tex
need john's proof
fixed abstract

\usepackage{array}
\usepackage{clrscode3e}
\usepackage{amsmath}
\usepackage{kbordermatrix}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage{svg}

@@

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We give an algorithm to efficiently calculate second degree polynomial or interaction 
that has complexity quadratically with respect to the density of the matrix, and can therefore be much faster than 
the naive approach and allows for the matrix to remain in sparse form. We apply the method
to several real datasets and give both analytical and empirical comparisons with the
naive approach.
\end{abstract}

@@

>>>>

\usepackage{array}
\usepackage{clrscode3e}
\usepackage{amsmath}
\usepackage{kbordermatrix}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage{svg}
\usepackage{pdfpages}

@@

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We give an algorithm to efficiently calculate second degree polynomial or interaction features for a sparse matrix.
The algorithm has average time complexity that decreases quadratically with respect to the density of the matrix, which
is a large improvement over the naive approach. It also allows for the matrix to remain in sparse form, reducing memory demands.
We apply the method to several real datasets and give both analytical and empirical comparisons with the
naive approach. The work also gives a generalizable method for creating algorithms for higher orders of polynomials.
\end{abstract}

@@

%Same as above, but in vector graphic form. Use this in the final.
%\begin{sidewaysfigure}
%    \centering
%    \includegraphics[scale=0.65]{classifier_boundaries.pdf}
%    \caption{Decision boundaries for four classifier types on four different datasets. The darker the color, the more certain the decision.
%             The plain dataset is shown in the first column. Each other column is a type of classifier applied to that dataset. The classifier
%             types are logistic regression, logistic regression with second degree polynomial features, RBF SVM, and gradient boosting with decision trees.
%             The accuracy of each model is shown in the bottom right corner of that model's subplot.}
%    \label{fig:boundaries}
%\end{sidewaysfigure}
